RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective

### 2022-11-25 main.tex
:lipstick: Update illustrations

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{colortbl}
% dark mode
% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

@@

\begin{document}
% \title{RIScatter: Unifying Scattering Techniques From a Distribution Perspective}
% \title{RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective}
% \title{RIScatter: Unifying BackCom and RIS From a Probabilistic Perspective}
% \title{RIScatter: Unifying Backscatter Communication, Symbiotic Radio, and Reconfigurable Intelligent Surface}
% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From an Input Distribution Perspective}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle
% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
% * cooperative input design can be used for co-located RIScatter nodes.
% * hardward to modulate using RIS is already available.
% * RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
% * Redefine RIS using book
% ? Using RIS to encode is not very interesting as controller is anyway usable
% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load switching speed is key for high data rate - symbol ratio is not very large
% TODO Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
% * channel coding: general non-adaptive (book) adaptive (DMC)
% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
% TODO semicoherent: known CSI, unknown primary/backscatter symbols
% * initialization, convergence
% * Base e, use 2 in simulation
% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
% ! SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
% * (I(X_1;Y_1),I(X_2;Y_2))
% ? Channel estimation error, coordination issues
% TODO  binary input and signal output (BISO) channel, ML figure

% ! add table row: adaptive to information source/csi/link weights
% ! explain link weights
% ! add table row: distributions
% ! table to sentences
% ! add primary and backscatter flows to illustrations
% ! discuss table and add challenges in contribution 1
% ! transition challenges (distribution and constellation-adaptive) to contribution 2, 3
% ! think RIScatter applications (use Rui's slides)
\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external radio wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{ris} adapts its phase shift response to enhance or suppress signal strength in specific directions.
	In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	Envisioned as a scatter protocol, RIScatter consists of multiple dispersed or co-located passive scatter nodes whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where reflection states are exclusively a function of information symbols (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detection region at the user.
	Simulation results demonstrate RIScatter nodes can exploit additional propagation path to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
\end{abstract}

@@

\begin{section}{Introduction}
	\begin{subsection}{Fundamentals}
		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
		% \cite{Liu2013b} proposed an \gls{ambc} system in Fig. \subref*{fg:ambc}, where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		\gls{ambc} was then proposed in \cite{Liu2013b} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum but is subject to the strong direct-link interference.
		To tackle this, \cite{Yang2018} proposed cooperative \gls{ambc} where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
		% The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
		The concept was further refined as \gls{sr} illustrated in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
		% In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates extra primary propagation path and superimposes its own message on the scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
		Those \gls{bc} applications employ scatter nodes as pure information sources such that the active primary link (if it exists) is influenced by backscatter randomness (often modelled as interference or channel uncertainty).
		On the other hand, \gls{ris} is a smart planar wave reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
		The reflection pattern is deterministic over time that can be optimized and coordinated before the transmission.
		\gls{ris} recycles and redistributes surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.
			\subfloat[\gls{mbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/mbc.tex}
				\label{fg:mbc}
			\subfloat[\gls{bbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/bbc.tex}
				\label{fg:bbc}
			\\
			\subfloat[\gls{ambc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ambc.tex}
				\label{fg:ambc}
			\subfloat[\gls{sr}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/sr.tex}
				\label{fg:sr}
			\\
			\subfloat[\gls{ris}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ris.tex}
				\label{fg:ris}
			\subfloat[RIScatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/riscatter.tex}
				\label{fg:riscatter}
			\caption{
				Illustration of scattering applications.
			\label{fg:scatter_illustration}

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabularx}{\textwidth}{CCCCCC}
			\toprule
			% \rowcolor{gray!25}
			                              & \gls{mbc}/\gls{bbc}       & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                                  & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                          & 2 (collaborative)                                 \\
			\rowcolor{gray!25}
			Scatterer contribution        & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                        & Backscatter modulation and passive beamforming    \\
			Cooperative transmissions     & ---                       & No (individual transmitters)                    & Active beamforming                           & ---                                        & Active beamforming and smart reflection           \\
			\rowcolor{gray!25}
			Cooperative reception         & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                        & Backscatter detection as primary channel training \\
			Primary detection             & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                   & Coherent                                          \\
			\rowcolor{gray!25}
			Backscatter detection         & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                        & Semi-coherent                                     \\
			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)            & Flexible (\gls{csi}- and traffic-adaptive)        \\
			\rowcolor{gray!25}
			Load-switching frequency      & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or quasi-static (blockwise) & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

	\begin{subsection}{Related Works}
		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
		% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
		% However, it assumed the primary and backscatter symbols of the same period are perfectly aligned in time.
		Joint \gls{ml} decoding provides the best error performance for \gls{sr} but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
		One special property of such an active-passive coexisting network is that the backscatter signal strength can be relatively weak due to the double fading effect.
		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
		% sequential primary-backscatter decoding based on \gls{sic}.
		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load switching speed typically varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}}.
		Such a sequential \gls{sic} involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol, which can be operation-intensive and \gls{csi}-sensitive.
		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection asymptotically approaches its coherent counterpart, and both links can be decoded in an interference-free manner \cite{Long2020a}.
		% However, the assumption of very large backscatter-over-primary symbol period ratio $N$ may not hold in practice\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
		Another open issue for \gls{bc} and \gls{sr} is efficient backscatter multiple access design.
		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
		\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy during others.
		It enables adaptive transmission time and reflection ratio optimization but incurs high coordination cost.
		\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
		This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher node power consumption.
		To reduce coordination burden for passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
		However, this code-domain solution suffers from the near-far problem and imperfect synchronization.

@@

		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
		As shown in Fig. \subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
		partially engineer the wireless channel and partially modulate its own information.
		This is accomplished by incorporating both the \gls{csi} and link weights into the reflection state distribution design.
		As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
		This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.
		% heterogeneous traffic control and universal hardware design

>>>>

\usepackage[table]{xcolor}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}
% dark mode
% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

@@

\begin{document}
\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Distribution Perspective}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE,}
		TODO
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx,TODO\}@imperial.ac.uk).
	}
}
\maketitle
% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
% * cooperative input design can be used for co-located RIScatter nodes.
% * hardward to modulate using RIS is already available.
% * RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
% ? RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
% * Redefine RIS using book
% x Using RIS to encode is not very interesting as controller is anyway usable
% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load-switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load-switching speed is key for high data rate - symbol ratio is not very large
% * Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
% * channel coding: non-adaptive (line-coding) or adaptive (DMC)
% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
% ? [mu-code]: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
% * backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
% ? semicoherent: known CSI, unknown primary/backscatter symbols
% * initialization, convergence, base 2 in simulation
% * SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
% * SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
% x when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
% ? Channel estimation error, coordination issues

% * add table row: adaptive to information source/csi/link weights
% * explain link weights
% * add table row: distributions
% * table to sentences
% * add primary and backscatter flows to illustrations
% ! discuss table and add challenges in contribution 1
% ! transition challenges (distribution and constellation-adaptive) to contribution 2, 3
% * think RIScatter applications (use Rui's slides)

\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	\gls{ris} adapts its phase shift response to enhance or suppress equivalent channel strength in specific directions.
	In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	Envisioned as a next-generation communication protocol, RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the equivalent channel of the existing link and partially modulate their own information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of both coexisting links.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific reflection states; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
\end{abstract}

@@

\begin{section}{Introduction}
	\begin{subsection}{Fundamentals}
		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
		% \cite{Liu2013b} proposed an \gls{ambc} system in Fig. \subref*{fg:ambc}, where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		\gls{ambc} was then proposed in \cite{Liu2013b} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum but is subject to the strong direct-link interference.
		To tackle this, \cite{Yang2018} proposed cooperative \gls{ambc} where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
		% The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
		The concept was further refined as \gls{sr} illustrated in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
		% In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates extra primary propagation path and superimposes its own message on the scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
		Those \gls{bc} applications employ scatter nodes as pure information sources such that the active primary link (if it exists) is influenced by backscatter randomness (often modelled as interference or channel uncertainty).
		On the other hand, \gls{ris} is a smart planar wave reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
		The reflection pattern is deterministic over time that can be optimized and coordinated before the transmission.
		\gls{ris} recycles and redistributes surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.

		\begin{figure}[!t]
			\centering
			\subfloat[\gls{mbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/mbc.tex}
				}
				\label{fg:mbc}
			}
			\subfloat[\gls{bbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/bbc.tex}
				}
				\label{fg:bbc}
			}
			\\
			\subfloat[\gls{ambc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ambc.tex}
				}
				\label{fg:ambc}
			}
			\subfloat[\gls{sr}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/sr.tex}
				}
				\label{fg:sr}
			}
			\\
			\subfloat[\gls{ris}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ris.tex}
				}
				\label{fg:ris}
			}
			\subfloat[RIScatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/riscatter.tex}
				}
				\label{fg:riscatter}
			}
			\caption{
				Illustration of scattering applications.
				The blue paths constitute the primary link while the magenta/green paths denote the backscatter link.
			}
			\label{fg:scatter_illustration}
		\end{figure}
	\end{subsection}

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\rowcolors{2}{gray!25}{white}
		\renewcommand{\arraystretch}{1.5}
		\begin{tabularx}{\textwidth}{CCCCCC}
			\toprule
			\hiderowcolors
			                                 & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
			\showrowcolors
			Coexisting link(s)               & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
			Backscatter modulation           & Yes                 & Yes                & Yes                                           & No                  & Yes                                                                     \\
			Scatterer impact on primary link & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
			Cooperative transmission(s)      & ---                 & No                 & Primary transmitter (active beamforming)      & ---                 & Primary transmitter and scatter nodes                                   \\
			Co-located receiver              & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
			Primary detection                & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
			Backscatter detection            & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
			Reflection pattern depends on    & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
			Input distribution               & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
			Load-switching speed             & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
		\end{tabularx}
	\end{table*}

	\begin{subsection}{Related Works}
		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
		% To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
		% However, it only considered the case where the primary and backscatter symbols of the same period are perfectly aligned in time.
		% However, it assumed the primary and backscatter symbols of the same period are perfectly aligned in time.
		Joint \gls{ml} decoding provides the best error performance for \gls{sr} but requires prohibitive computational complexity especially for high-order modulations \cite{Yang2018}.
		One special property of such an active-passive coexisting network is that the backscatter signal strength can be relatively weak due to the double fading effect.
		It motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
		% sequential primary-backscatter decoding based on \gls{sic}.
		During primary decoding, the backscatter randomness can be modelled as either interference or channel uncertainty, depending on the ratio $N$ of primary sampling rate over backscatter load-switching speed\footnote{For state-of-the-art low-power \gls{rfid} tags, the load-switching speed typically varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}}.
		Such a sequential \gls{sic} involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol, which can be operation-intensive and \gls{csi}-sensitive.
		When $N$ is sufficiently large (i.e., commensal \gls{sr}), the average primary achievable rate under noncoherent detection asymptotically approaches its coherent counterpart, and both links can be decoded in an interference-free manner \cite{Long2020a}.
		% However, the assumption of very large backscatter-over-primary symbol period ratio $N$ may not hold in practice\footnote{For example, Wi-Fi sampling rate is \qty{20}{\MHz} while \gls{rfid} load-switching speed varies between \num{100}s of \unit{\kHz} to \num{10}s of \unit{\MHz} \cite{Torres2021}, corresponding to a typical $N$ between \num{1} and \num{100}.}, and such a \gls{sic}-based sequential decoding requires re-encoding, precoding, and subtraction at each primary symbol block with a time-domain \gls{mrc}, which can be operation-intensive and \gls{csi}-sensitive.
		Another open issue for \gls{bc} and \gls{sr} is efficient backscatter multiple access design.
		\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} where the \gls{sic} order depends on the backscatter channel strength, but the performance deteriorates fast as the number of nodes increases.
		\gls{tdma}-based \gls{sr} was also considered in \cite{Yang2021a} where each node transmits information during its dedicated slot and harvests energy during others.
		It enables adaptive transmission time and reflection ratio optimization but incurs high coordination cost.
		\cite{Vougioukas2019} modifies the load-switching speed to shift the scattered signal to the desired frequency band.
		This enables backscatter \gls{fdma} at the cost of extra bandwidth and higher node power consumption.
		To reduce coordination burden for passive nodes, \cite{Han2021} proposed a random code-assisted multiple access for \gls{sr} and evaluated the asymptotic \gls{sinr} using random matrix theory.
		However, this code-domain solution suffers from the near-far problem and imperfect synchronization.

@@

		\emph{First,} we propose RIScatter as a novel scatter protocol that unifies \gls{bc} and \gls{ris} from a distribution perspective.
		As shown in Fig. \subref*{fg:riscatter}, the passive RIScatter node rides over an active transmission and controls the scattered wave to
		partially engineer the wireless channel and partially modulate its own information.
		This is accomplished by incorporating both the \gls{csi} and \gls{qos} into the reflection state distribution design.
		As such, RIScatter can generalize \gls{bc} (uniform distribution) and \gls{ris} (degenerate distribution) to create a tradeoff between backscatter modulation and passive beamforming.
		This is the first paper to associate \gls{bc} and \gls{ris} from a distribution perspective.
		% heterogeneous traffic control and universal hardware design
